---
name: Ryan
surname: Safner
position: "Assistant Professor of Economics"
address: "George B. Delaplaine Jr. School of Business, Hood College, Frederick, MD"
# profilepic: "img/summer_2019.jpg"
# phone: +1 301 696 3368
www: ryansafner.com
email: "safner@hood.edu"
twitter: ryansafner
github: ryansafner
# linkedin: ryansafner
# googlescholar: GDbo0gsAAAAJ
# orcid: 0000-0002-6177-9308
# extrainfo: "testing extra info"
# quote: "testing a quote"
headcolor: e64173 #009ACD
#urlcolor: e64173
date: "`r format(Sys.time(), '%B %Y')`"
docname: CV
# about me: "Testing About Me"
output: vitae::awesomecv
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(fontawesome)
library(tidyverse)
```

# \faBriefcase \acvHeaderIconSep Academic Appointments

```{r}
tribble(
  ~ title, ~ year, ~ institution, ~ where,
  #"Hood College", "2019—", "Assistant Professor of Economics", "Frederick, MD", "Assistant Professor of Economics",
  #"Hood College", "2016—2019", "Visiting Assistant Professor of Economics", "Frederick, MD", "Visiting Assistant Professor of Economics",
  #"Hood College", "2016—", "Assistant Professor of Economics", "Frederick, MD", "2019—",
  #"Hood College", "2016—", "Visiting Assistant Professor of Economics", "Frederick, MD", "2016—2019",
  "Assistant Professor of Economics", "2019—Present", "Hood College", "Frederick, MD",
  "Visiting Assistant Professor of Economics", "2016—2019", "Hood College", "Frederick, MD",
  "Visiting Assistant Professor of Economics", "2015—2016", "Wake Forest University", "Winston-Salem, NC",
  "Adjunct Lecturer", "2015", "George Mason University", "Fairfax, VA",
  "Graduate Lecturer", "2013—2015", "George Mason University", "Fairfax, VA"
) %>% 
  detailed_entries(with = title,
                   what = institution,
                   #why = detail,
                   when = year,
                   where = where)
```


# \faGraduationCap \acvHeaderIconSep  Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Ph.D — Economics", "2015", "George Mason University", "Fairfax, VA",
  "M.A. — Economics", "2013", "George Mason University", "Fairfax, VA",
  "B.A. — Economics", "2011", "University of Connecticut", "Storrs, CT"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# \faFlask \acvHeaderIconSep Research

## \faExclamationTriangle \acvHeaderIconSep Interests

Public goods, innovation & technological growth, and intellectual property, using the tools of game theory, new institutional economics, market process economics, and public choice

\medskip

## \faFile \acvHeaderIconSep Peer-Reviewed Journal Articles

```{r}
bibliography_entries("publications.bib") %>%
  arrange(desc(issued))
```

\bigskip

## \faWrench \acvHeaderIconSep Under Review

```{r}
bibliography_entries("underreview.bib") %>%
  arrange(desc(author$family), issued)
```

\bigskip 

## \faSpinner \acvHeaderIconSep Works in Progress

```{r}
bibliography_entries("workingpapers.bib") %>%
  arrange(desc(author$family), issued)
```

# \faUniversity \acvHeaderIconSep Teaching

## Summary

I have taught a wide variety of economics electives and principles courses. At Hood college, I regularly teach intermediate microeconomics (every semester), econometrics (every fall), and an economics elective each semester. See also [my blog](http://ryansafner.com/post/) for posts relevant to teaching and pedagogy, particularly related to econometrics, data science, and workflow

## Hood College

- ECMG 212 — Statistics for Economics & Management (S2017)
- ECON 205 — Principles of Macroeconomics (F2018)
- ECON 304 — International Political Economy (F2017) 
- ECON 306 — Microeconomic Analysis (F2016; S2017; F2017; S2018; F2018; S2019; F2019; S2020; [F2020](https://microf20.classes.ryansafner.com); S2021)
- ECON 315 — Economics of the Law^[Designed and created course] (S2021)
- ECON 316 — Game Theory (S2019)
- ECON 317 — Economics of Development ([F2019](https://devf19.classes.ryansafner.com))
- ECON 324 — International Trade (F2016; F2018; [Fall 2020](https://tradef20.classes.ryansafner.com))
- ECON 326 — Industrial Organization (S2017; [Spring 2020](https://ios20.classes.ryansafner.com))
- ECON 410 — Public Economics (S2018; [Spring 2020](https://publics20.classes.ryansafner.com))
- ECON 452 — History of Economic Thought ([F2020](https://thoughtf20.classes.ryansafner.com))
- ECON 480 — Econometrics (F2016; F2017; F2018; F2019; [F2020](https://metricsf20.classes.ryansafner.com))
- MGMT 399 — Internship for Business (S2018)

## Wake Forest University

- ECN 150 — Introduction to Economics (Fall 2015; Spring 2016)
- ECN 271 — Special Topics: Austrian Economics (Spring 2016)

## George Mason University

- ECON 385 —  International Economic Policy (Summer 2013, Fall 2013, Spring 2014)
- ECON 403 — Austrian Economics (Summer 2015)
- ICES — High School Economics Workshops (Summer 2012, cotaught with Paul Mueller)

# \faComments \acvHeaderIconSep Talks

- 2019, "A Tale of Two Capitals," *Southern Economic Association* Annual Conference, Fort Lauderdale, FL. 
- 2019, "Magic Internet Money? How Blockchain Technology Might Revolutionize the 21st Century Economy," *Phi Kappa Phi* Lecture, Hood College
- 2018, "Distributing Patronage: Intellectual Property in the Transition from Natural State to Open Access Order," *Southern Economic Association* Annual Conference, Washington, DC.
- 2017, "The Network Origins of Economic Growth", *Southern Economic Association* Annual Conference, Tampa, FL.
- 2016, "Ideas, Institutions, and Technological Progress," *Southern Economic Association* Annual Conference, Washington, DC.
- 2015, "Institutional Entrepreneurship, Wikipedia, and the Opportunity of the Commons," *Southern Economic Association* Annual Conference, New Orleans, LA.
- 2015, "Pirate Thy Neighbor: The Protectionist Roots of International Copyright," *Public Choice Society* Annual Conference, San Antonio, TX.
- 2015, "Wiki-nomics: Bringing Institutions Back into Copyright Analysis with a Case Study of Wikipedia," *Public Choice Society* Annual Conference, San Antonio, TX.
- 2014, "Crowdfunding Creative Goods, Crowding out Intellectual Property?" *Southern Economic Association* Annual Conference, Atlanta, GA.
- 2014, "Learning by Doing: Who's Learning? Who's Doing? and other Production Function Myths," (with Santiago Gangotena), *Southern Economic Association* Annual Conference, Atlanta, GA.
- 2014, "'Public Goods' or  'Good for the Public?' - Endogenizing Public Goods," *Association of Private Enterprise Education* Annual Conference, Las Vegas, NV.
- 2014, "A Structural Analysis of Regulatory Capitalism" (with Julia Norgaard and Vlad Tarko), *Association of Private Enterprise Education* Annual Conference, Las Vegas, NV.
- 2014, "Democracy and Political Cost - A Framework for Understanding Political Entrepreneurship in an Entangled Political Economy", *Public Choice Society* Annual Conference, Charleston, SC.
- 2013, "Copyright Since 1976: An Interventionism Framework," *Southern Economic Association* Annual Conference, Tampa, FL.
- 2013, "Towards an Institutional View of Ideas, Copyright, and Piracy," *Institute for Humane Studies*: Symposium on Scholarship and a Free Society, Arlington, VA.

# Professional Development

- 2014, *Institute for Humane Studies* and *The Liberty Fund, Inc.* Advanced Topics Seminar: City-States as an Alternative to Nation States. Arlington, VA
- 2013, *Institute for Humane Studies*: Symposium on Scholarship and a Free Society. Arlington, VA
- 2012, *Institute for Humane Studies* and *The Liberty Fund, Inc.* Advanced Topics Seminar: The Growth of Government. Arlington, VA
- 2012, *Institute for Humane Studies* Advanced Studies Seminar: The Challenges and Future of Liberty. Arlington, VA
- 2012, *Institute for Humane Studies* Workshop: Career Development Workshop. Arlington, VA


# \faTrophy \acvHeaderIconSep Academic Awards and Grants

- Hood College Center for Teaching Academic Innovation Grant 2019
- Hood College Board of Associates McCardell Professional Development Grant 2018
- Hood College Board of Associates McCardell Professional Development Grant 2017
- F. A. Hayek Fund for Scholars (Institute for Humane Studies) 2015
- F. A. Hayek Fund for Scholars (Institute for Humane Studies) 2014
- Earhart Foundation Fellowship 2014-2015
- Mercatus Center Graduate Student Summer Research Fellowship 2014
- Graduate Student Travel Fund Grant (George Mason University) 2014
- Earhart Foundation Fellowship 2013-2014
- F. A. Hayek Fund for Scholars (Institute for Humane Studies) 2013
- Dunn Foundation Fellowship 2012-2013


# \faBriefcase \acvHeaderIconSep Consulting

- Member of City of Frederick Mayor's Strategic Opportunities Advisory Team, Economic Resilience Work Group, Ted Gregory, chair (2018) 	

# \faUsers \acvHeaderIconSep Service

## To Hood College

- Member of Curriculum Committee (Fall 2018—Spring 2020)
    - Committee Chair (Fall 2019—Spring 2020)
- Member of SPIRES Committee (Fall 2019—Spring 2020)
- Chaired search committee for Visiting Assistant Professor of Economics (2019-2020) position (successful hire)
- Taught mini-course "Magic Internet Money? How Blockchain Technology Could Revolutionize the 21st Century Economy," Accepted Students Day, April 6, 2019
- Panel discussant for "The EU: Dead At 60?" Panel, Hood College, September 7, 2018
- Created and approved new economics course: ECON 315 — Economics of the Law (2020)
- Proposed change to Economics major, approved by the Curriculum Committee (Spring 2018)
- Taught mini-course "A Pirate's Life for Me — The Economics of Intellectual Property and (Digital) Piracy", Accepted Students Day, April 11, 2018
- Taught mini-course "A Pirate's Life for Me — The Economics of Intellectual Property and (Digital) Piracy", Accepted Students Day, April 8, 2017
- Panel discussant for "Globalization and Its Discontents" Panel, Hood College, March 2, 2017
- Committee chair for Departmental Honors Thesis undergraduate students:
  - Natalie Kolosieke (2020—2021)
  - Kevin Ciocco (2020—2021)
  - Valentin Donchev (2019—2020)
  - Emily Stubits (2019—2020)
  - Elias Nicholson (2018—2019)
    - Nicholson, Elias, 2019, "Regulation and Discrimination: Race and Interest Rate Mark-Ups in the Auto Loan Industry," [*Issues in Political Economy*](https://blogs.elon.edu/ipe/issues/volume-28-issue-1/) 28(1)
  - Zack Miller (2016—2017)
- Committee member for Departmental Honors Thesis undergraduate students:
  - Jared Knowles (2016-2017)
  - Jaclyn Bealer (2016-2017)
- Department Library Liason (Fall 2016--Present)

## To Wake Forest University

- Committee member for Senior Thesis undergraduate student Adrian Martino (WFU, 2016);

## To the Profession

- Reviewer for *Journal of Institutional Economics*, *European Journal of Law and Economics*, and *Review of Austrian Economics* 
- Faculty reviewer for *Institute for Humane Studies*' Humane Studies Fellowships (2016, 2017)

## \faGroup \acvHeaderIconSep Professional Memberships

- Society for the Development of Austrian Economics
- Southern Economic Association
- American Economic Association
- Phi Kappa Phi Honor Society

# \faCogs \acvHeaderIconSep Skills

```{r, results = "asis", eval = F}
library(fontawesome)
stars<-as.character(fontawesome::fa("star"))
tribble(
  ~"", ~"",
  "R", stars,
  "Stata", stars
) %>%
  knitr::kable(booktabs = T, align = 'lr', escape = F, format = "latex")
```

- **Languages**:
  - English \faStar \faStar \faStar \faStar
  - Russian \faStar \faStar \faStarO \faStarO
  - Spanish \faStar \faStar \faStar \faStarO
- **Software**:
  - R: \faStar \faStar \faStar  \faStarHalfEmpty
  - Stata: \faStar \faStar \faStar \faStarHalfEmpty